Assessing rigor and impact of research software for hiring and promotion in psychology: A comment on Gärtner et al.~(2022)

### 2023-10-04 manuscript.Rmd
remove note, add other sections

note: |
  A commentary on:
  Gärtner, A., Leising, D., & Schönbrodt, F. D. (2022, November 25). Responsible Research Assessment II: A specific proposal for hiring and promotion in psychology. https://doi.org/10.31234/osf.io/5yexm

  Submitted to Meta-Psychology.

  Participate in open peer review by commenting through hypothes.is directly on this preprint. The full editorial process of all articles under review at Meta-Psychology can be found following this link: https://tinyurl.com/mp-submissions. You will find this preprint by searching for the first author’s name.

@@

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

>>>>

@@

## Author Contact

Put the contact information and any acknowledgements here. ORCID to all author if available. Corresponding author mandatory.
These headings after the article but before the references are required. Feel free to add other headings (e.g., acknowledgments) if you need to.

## Conflict of Interest and Funding

Add a statement about conflict of interest. If you have no conflict of interest to declare, please state that. Add a statement about how the research was funded. If there was no specific funding please state that.

## Author Contributions

Explain the contribution of each authors. If you are the single author, please spell it out anyway for future proper credit of your contributions and meta-science studies. 
The Contributor Roles Taxonomy can be helpful. https://www.casrai.org/credit.html 
Please explain how the author names order connects to the contribution (e.g. alphabetical, ranked, or random order).

## Open Science Practices

 \includegraphics[scale=0.50]{badges/opendata.png}
 \includegraphics[scale=0.50]{badges/openmaterial.png}
 \includegraphics[scale=0.50]{badges/preregestered.png}
 \includegraphics[scale=0.50]{badges/preregesteredplus.png}

\textbf{NOTE. This will be filled out by the reproducibility team.}
This article earned the Preregistration, Open Data and the Open Materials badge for preregistering the hypothesis and analysis before data collection, and for making the data and materials openly available. It has been verified that the analysis reproduced the results presented in the article. The entire editorial process, including the open reviews, are published in the online supplement.
